Temporal stability in human interaction networks

### 2015-08-20 paper.tex
adicionadas modificacoes entregues pelo leo
alocadas revisoes na pasta proprio

Network types have been discussed with regard to the number of participants, intermittence of their activity and network longevity~\cite{barabasiEvo}. Two topologically different networks emerged from human interaction networks, depending on the frequency of interactions, which can either be a generalized power law or an exponential connectivity distribution~\cite{barabasiTopologicalEv}. In email list networks, scale-free properties were reported with $\alpha=1$~\cite{bird} (as are web browsing and library loans~\cite{barabasiHumanDyn}), and different linguistic traces were related to weak and strong ties~\cite{GMANE2}.

@@

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.5\textwidth]{figs/fser_}
	\caption{Classification of the scale-free network vertices by comparing the degree
		distribution against that of an Erd\"os-R\'enyi ideal network.
		The latter has more intermediary vertices, while the former has more peripheral and hub vertices.
		The sector borders are defined by the two intersections $k_L$ and $k_R$ of the connectivity distributions.
		Characteristic degrees are in the compact intervals: $[0,k_L]$, $(k_L,k_R]$, $(k_R,k_{max}]$ for the Erd\"os sectors (periphery, intermediary and hubs).}
		\label{fig:setores}
\end{figure}
To ensure statistical validity of the histograms, bins can be chosen to contain at least $\eta$ vertices of the real network. The range $\Delta$ of incident values should be partitioned in $m$ parts $\Delta=\cup_{i=1}^m \Delta_i$, with $\Delta_i\cap \Delta_j \; \forall\; i \neq j$. Thus, $\Delta_i=\{max(\Delta_{i-1})<k\leq j \;\;|\; \sum_{\Delta_{i-1}+1}^j \eta_k > \eta \}$, with $\eta_k$ the number of vertices with degree $k$ and $max(\Delta_{0})=-1$.This changes equation~\ref{criterio} to

\begin{equation}\label{criterio2}
	\begin{split}
	\sum_{x=min(\Delta_i)}^{max(\Delta_i)} \widetilde{P}(x) < \sum_{x=min(\Delta_i)}^{max(\Delta_i)} P(x) \Rightarrow \\
	\Rightarrow \Delta_i \text{ hods intermediary degree values.}
	\end{split}
\end{equation}

@@

The simplification of all possible compound possibilities to the small set listed above can be formalized in strict mathematical terms, but this was considered out of scope for current interests. It is worth noting that the exclusivist cascade is the same sectioning of an inclusivist cascade from periphery to hubs, but with inverted order of sectors. These compound criteria can be used to examine network sections considering all degrees and strengths and are especially useful in the case of a low number of messages, such as in Section~\ref{si:frac} of the Supporting Information.

>>>>

Network types have been discussed with regard to the number of participants, intermittence of their activity and network longevity~\cite{barabasiEvo}. Two topologically different networks emerged from human interaction networks, depending on the frequency of interactions, which can either be a generalized power law or an exponential connectivity distribution~\cite{barabasiTopologicalEv}. In email list networks, scale-free properties were reported with $\alpha \approx 1.8$~\cite{bird} (as are web browsing and library loans~\cite{barabasiHumanDyn}), and different linguistic traces were related to weak and strong ties~\cite{GMANE2}.

@@

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.5\textwidth]{figs/fser_}
	\caption{Classification of the scale-free network vertices by comparing the degree
		distribution against that of an Erd\"os-R\'enyi ideal network.
		The latter has more intermediary vertices, while the former has more peripheral and hub vertices.
		The sector borders are defined by the two intersections $k_L$ and $k_R$ of the connectivity distributions.
		Characteristic degrees are in the compact intervals: $[0,k_L]$, $(k_L,k_R]$, $(k_R,k_{max}]$ for the Erd\"os sectors (periphery, intermediary and hubs).}
		\label{fig:setores}
\end{figure}
To ensure statistical validity of the histograms, bins can be chosen to contain at least $\eta$ vertices of the real network. The range $\Delta$ of incident values should be partitioned in $m$ parts $\Delta=\cup_{i=1}^m \Delta_i$, with $\Delta_i\cap \Delta_j \; \forall\; i \neq j$. Thus, $\Delta_i=\{max(\Delta_{i-1})<k\leq j \;\;|\; \sum_{max(\Delta_{i-1})+1}^j \eta_k \geq \eta \text{ and } (\sum_{max(\Delta_{i-1})+1}^{j-1} \eta_k < \eta \text{ or } j=max(\Delta_{i-1})+1) \}$, with $\eta_k$ the number of vertices with degree $k$ and $max(\Delta_{0})=-1$. This changes equation~\ref{criterio} to

\begin{equation}\label{criterio2}
	\begin{split}
	\sum_{x=min(\Delta_i)}^{max(\Delta_i)} \widetilde{P}(x) < \sum_{x=min(\Delta_i)}^{max(\Delta_i)} P(x) \Rightarrow \\
	\Rightarrow \Delta_i \text{ holds intermediary degree values.}
	\end{split}
\end{equation}

@@

The simplification of all possible compound possibilities to the small set listed above can be formalized in strict mathematical terms, but this was considered out of scope for current interests. It is worth noting that the exclusivist cascade is the same sectioning of an inclusivist cascade from periphery to hubs, but with inverted order of sectors. These compound criteria were used to examine network sections considering all degrees and strengths and are especially useful in the case of a low number of messages, such as in Section~\ref{si:frac} of the Supporting Information.
